Algebraic File Synchronization: Adequacy and Completeness

### 2016-12-02 p2/ordering.tex
Improved text

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence $U$,
we use $\orderset{U}$ to denote the set of sequences
that are all permutations of the commands in $U$
for which the following holds:
for any two commands $\cxynv$ and $\czwmv$ in a sequence in $\orderset{U}$
where $\cxynv$ comes earlier in the sequence than $\czwmv$,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

The principal ideas behind this algorithm are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on parent and child nodes;
and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating the pairs we see that they are identified by the output value of the first command ($y$),
and that they determine whether the command on the parent or the child must precede the other.

@@

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but it contains commands that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2 \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

@@

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
Let the first command in $S$ be $\cxynv$, that is, $S=\cxynv\cc S_0$.
We proceed by a nested induction on the number of commands before $\cxynv$ in $T$.
Our base case is when it is the first command, which means $T=\cxynv\cc T_0$.
Then from \cref{subseq_in_orderset} we know $T_1\in\orderset{S_0}$
and from the induction hypothesis $T_0\equiv S_0$ from which we get $T\equiv S$.

>>>>

\begin{mydef}[$\ordersetsign$]\label{def_orderset}
For a simple set or sequence $U$,
we use $\orderset{U}$ to denote the set of sequences
that are all permutations of the commands in $U$
for which the following holds:
for any two commands $\cxynv$ and $\czwmv$ in a permutation
where $\cxynv$ comes earlier,
\begin{itemize}
\item if $n=\parent(m)$, then $y=\vald$
\item if $\parent(n)=m$, then $y=\empt$.
\end{itemize}
\end{mydef}

The principal ideas behind this algorithm are 
\cref{ax_separate_commute}, from which we know that commands on incomparable
nodes can be applied in any order, so we only need to focus on the order of commands
with comparable nodes;
\cref{connected_changes}, from which we know that if $U$ contains commands on two comparable
nodes, then it contains commands on all nodes in between, so it is enough to specify
the order of commands on directly related nodes;
and finally, \cref{ax_directchild_breaks,ax_directparent_breaks}, from which we know
that commands on parent--child pairs must be construction or destruction pairs.
Investigating these pairs we see that they are identified by the output value of the first command ($y$),
which in turn determines whether the command on the parent or the child must precede the other.

@@

% BACK_TO_THE_FS TODO
% TODO Review any proof depending on "nothing changes FS at n until...".
Formally, we prove our proposition by contradiction,
and in this version of the proof we reach back to our filesystem model.
We assume $S\nequiv\cbrk$ and therefore there is a $\FS$ for which $S\aFS\neq\fsbroken$,
but it contains commands on a node and its parent that do not form a construction or destruction pair.
Select two such commands, $\cxynv$ and $\czwmv$,
and split $S$ around them into three parts:
\[ S = S_0 \cc \cxynv \cc S_1 \cc \czwmv \cc S_2 \]
As $S$ is simple, there cannot be any commands on $n$ or $m$ in $S_1$,
and therefore $(S_0\cc\cxynv\cc S_1)\FS(n) = y$,
and $[(S_0\cc\cxynv\cc S_1)\FS(m)] = [S_0\FS(m)]$.
If $[z]\neq[S_0\FS(m)]$, then $S\aFS=\fsbroken$, which is a contradiction.

@@

Let us consider $T\in\orderset{S}$ where $T$ and $S$ are of length $i+1$.
Let the first command in $S$ be $\cxynv$, that is, $S=\cxynv\cc S_0$.
We proceed by a nested induction on the number of commands before $\cxynv$ in $T$.
Our base case is when it is the first command, which means $T=\cxynv\cc T_0$.
Then from \cref{subseq_in_orderset} we know $T_0\in\orderset{S_0}$
and from the induction hypothesis $T_0\equiv S_0$ from which we get $T\equiv S$.
